---
title: "Asynchronous assignment"
author: "Jyosna Philip"
date: "2023-12-21"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Two bonding agents, A and B, are available for making a laminated beam. Out of 50 beams
made with Agent A, 11 failed a stress test, whereas 19 of the 50 beams made with Agent B failed. At the 0.05 level, can we conclude that the performance of Agent A is same as Agent B?

p1=proportion of failed bonding agents of type A
p2=proportion of failed bonding agents of type B
```{r}
p1=11/50
p2=19/50


```
sucess=failed bonding agents of type A
success=failed bonding agents of type B

```{r}
x=c(11,19)
n=c(50,50)
```
H0: p1=p2 (Performance of agent A is same as agent B)
H1: p1!=p2 (Performance of agent A is not same as agent B)

```{r}
#library(dplyr)
prop.test(x,n,alternative='two.sided',conf.level=0.95)
```
Since p-value is greater than 0.05(which is our significance level), we fail to reject H0.
Therefore,we can conclude that the performance of Agent A is same as Agent B
