---
title: "Lab 08"
author: "Jyosna Philip"
date: "2024-01-18"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Aim: 
To find the difference between the theoretical and practical rendition of goodness of fit test.

Qs. Suppose you are analysing the distribution of the preferred programming languages among a group of 500 data science students. You have collected data and observed the following distribtution:
Python: 300
R: 120
Java: 40
Other: 40
Now the theoretical distribution based on your expectation is as follows(in proportions):
Python: 0.56(56%)
R: 0.2(20%)
Java: 0.1(10%)
Other: 0.14(14%)

1. Evaluate whether the observed values of preferred programming languages align with the expectation?
2. Find the expected values and the residuals?



```{r}
observed=c(300,120,40,40)
prob=c(0.56,0.2,0.1,0.14)
m=chisq.test(observed,p=prob)
m
```
We get chi-squared value as 20.286 and p-value 0.00014. Since pvalue is less than 0.05 we reject H0 and conclude that the observation doesn't align with the expected values.

```{r}
m$expected
```
280,100,50 and 70 are the expected values of Python,R,Java and other languages respectively.
```{r}
m$residuals #residuals are differenc ebetween predicted and actual values 
```
1.19, 2,-1.4,-3.58 are the residuals associated with Python,R,Java and other languages respectively.

Conclusion: pvalue<0.05,Hence we conclude that the preference doesnt align with the expectations.


#Notebook Questions
Q1. test the hypothesis that the no of parts in demand doesnt depend on the type of day
H0:no of parts in demand doesnt depend on the type of day
h1:no of parts in demand depend on the type of day
```{r}
observed=c(1124,1125,1110,1120,1126,1115)
prob=c(1/6,1/6,1/6,1/6,1/6,1/6)
chisq.test(observed,p=prob)
```
We get chi-squared value is 0.18 and p-value as 0.99.
Conclusion: since p value>0.05 we conclude that there is no dependency of parts on demand and type of day.

# CONCLUSION
Goodness of fit test was carried out for the given questions both practically and theoretically and the results were compared.


