---
title: "Lab 07"
author: "Jyosna Philip"
date: "2024-01-09"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# INTRODUCTION
We aim for the examination of data dispersion within a singular group and the rigorous comparison of variances between two distinct populations. These can be done using chi squared test and f test respectively.

# TESTING VARIANCE OF SINGLE POPULATION  
To test the variance of single population, chi square test is used. The library required for this is imported.

```{r}
library(EnvStats)
```
# Importing Dataset

# Dataset Description

This dataset contains online shopping data,and details regarding the use of discount coupons.
```{r}
online_shopping <- read.csv("C:/Users/jyosn/Downloads/archive (2)/online_shopping.csv")
online_shopping<- na.omit(online_shopping)
head(online_shopping)
tail(online_shopping)
```

# Target Variable 
Our target variable is Avg_Price.

# POPULATION
```{r}
population=online_shopping$Avg_Price
```
```{r}
pop_var=var(population)
pop_var
```

#Sample
```{r}
s=sample(population,150,replace=FALSE)

```

# CHI-SQUARE TEST FOR SINGLE MEAN
 H0: Variance of Avg_Price of all transactions 4000
 H1: VAriance of Avg_Price of all transactions !=4000
 
```{r}
varTest(s,alternative = "two.sided",sigma.squared = 4000)
```
Since p-value is 0.38 and thus greater than 0.05, we fail to reject H0.
Hence variance of the population, that is , variance of avg_price of all transactions is 4000.

# CONCLUSION
We have carried out chi-square test for test of variance for single population. Our p-value came out greater than 0.05 and thus we can conclude that the variance of avg_price of all transactions is 4000.

# TESTING EQUALITY OF VARIANCES

Here our target variables are avg_price of male and females respectively.
# GETTING POPULATIONS
```{r}
popMale=subset(online_shopping,Gender=='M')
popMale1=popMale$Avg_Price
popFemale=subset(online_shopping,Gender=='F')
popFemale1=popFemale$Avg_Price
```
# GETTING SAMPLES
```{r}
sMale=sample(popMale1,150,replace=TRUE)
sFemale=sample(popFemale1,150,replace=TRUE)
```

## COMPARING VARIANCES OF TWO POPULATION
TWO-SIDED TEST
H0: Variances of Avg_Price spend by Males and Females are equal
H1: Variances of Avg_Price spend by Males and Females are not equal

```{r}
var.test(sMale,sFemale,alternative = "two.sided",conf.level = 0.95)
```
p-value is less than 0.05, Hence we reject H0.
The variances are not equal.

RIGHT-SIDED HYPOTHESIS TEST
H0: Variances of Avg_Price spend by Males and Females are equal
H1: Variances of Avg_Price spend by Males is greater than Females
```{r}
var.test(sMale,sFemale,alternative = "greater",conf.level = 0.95)
```
p-value is 0.016<0.05, Hence we  reject H0. The variance of avg_price spend by males is significantly greater than that of females.

# CONCLUSION
We used F-Test to compare the variance of two population,here, it was to compare the variance of avg_price spent by males and females. During right-tailed hypothesis test, our p-value was less than 0.05. Hence we can conclude that the variance of avg_price spend by males is significantly greater than that of females.



