---
title: "Lab 03"
author: "Jyosna Philip"
date: "2023-12-07"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Test of equality of two means when known σ.
# Dataset
Description: the data provides rating for samples of Arabica coffee from many places.
```{r}

arabica_data_cleaned <- read.csv("C:/Users/jyosn/Downloads/arabica_data_cleaned.csv")

```

```{r}
dim(arabica_data_cleaned)
```
There are 1311 entries(rows) and 43 attributes(columns).
```{r}
head(arabica_data_cleaned)
tail(arabica_data_cleaned)

```
# Taking 'Brazil' as target 1 variable
```{r}
target1<-subset(arabica_data_cleaned,Country.of.Origin==c("Brazil"))

```
# Taking 'Colombia' as target 2 variable
```{r}
target2<-subset(arabica_data_cleaned,Country.of.Origin==c("Colombia"))
```
 ## Mean and SD of Target 1 Population
 
```{r}
mean_pop1=mean(target1$Flavor)
mean_pop1
sd_pop1=sd(target1$Flavor)
sd_pop1

```
 Population Mean of Brazilian coffee Flavor is 7.57 and population standard deviation is 0.277.

 ## Mean and SD of Target 2 Population
 
  
```{r}
mean_pop2=mean(target2$Flavor)
mean_pop2
sd_pop2=sd(target2$Flavor)
sd_pop2

```
Population Mean of Colombian coffee Flavor is 7.57 and population standard deviation is 0.277.

# Sample of Target 1 Population

```{r}
sample1=sample(target1$Flavor,100,replace=FALSE)
mean(sample1)
sd1=sd(sample1)
sd1
```
Mean and sd of target 1 sample is 7.48 and 0.39 respectively.

# Sample of Target 2 Population

```{r}
sample2=sample(target2$Flavor,100,replace=FALSE)
mean(sample2)
sd2=sd(sample2)
sd2
```
Mean and sd of target 1 sample is 7.62 and 0.31 respectively.

IMPORTING BSDA LIBRARY FOR Z TEST FUNCTION.
```{r}
library(BSDA)
```


# TWO TAILED TEST
Two check if the mean flavor value of Brazilian and Colombioan coffee  are same.
H0: mu1=mu2
H1: mu1!=mu2
```{r}
z.test(x=sample1,y=sample2,alternative = "two.sided",mu=0,sigma.x = sd1,sigma.y=sd2,conf.level = 0.95)
```
Interpretation: z=-1.31. as it is greater than -1.96(the critical value at 5% significance level), and since p-value=0.299 is greater than 0.05 ,we fail to reject H0.
Hence the difference of mean value of Flavour and Aroma rating atrributes of the Arabica coffee is not statistically significant.

# ONE-TAILED TEST(Left-tailed)

To check if mean flavor rating is less than aroma ratings.
H0: mu1=mu2
H1: mu1<mu2
```{r}
z.test(x=sample1,y=sample2,alternative = "less",mu=0,sigma.x = sd1,sigma.y=sd2,conf.level = 0.95)
```
Interpretation: z=-1.04. as it is greater than -1.64(the critical value at 5% significance level), and since p-value=0.14 is greater than 0.05 ,we fail to reject H0.
Hence the difference of mean value of Flavour and Aroma rating atrributes of the Arabica coffee is not statistically significant.

# ONE-TAILED TEST(Right-tailed)

To check if mean flavor rating is greater than aroma ratings.
H0: mu1=mu2
H1: mu1>mu2
```{r}
z.test(x=sample1,y=sample2,alternative = "greater",mu=0,sigma.x = sd1,sigma.y=sd2,conf.level = 0.95)
```
Interpretation: z=-1.04. as it is less than 1.64(the critical value at 5% significance level), and since p-value=0.85 is greater than 0.05 ,we fail to reject H0.
Hence the difference of mean value of Flavour and Aroma rating atrributes of the Arabica coffee is not statistically significant.


