---
title: "Lab 04"
author: "Jyosna Philip"
date: "2023-12-15"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## AIM
Test for proportion of single population (large samples) 




## DATASET DESCRIPTION
This dataset contains information on bone tumors. The data was collected from patients at the Memorial Sloan Kettering Cancer Center (MSKCC). 
```{r cars}
Bone_Tumor <- read.csv("C:/Users/jyosn/Downloads/archive (1)/Bone Tumor Dataset.csv")

```
## ANALYSIS
```{r}
head(Bone_Tumor)
tail(Bone_Tumor)
```
```{r}
dim(Bone_Tumor)
```
This dataset has 9 attributes and 500 rows.

```{r}
summary(Bone_Tumor)
```
All attributes are of character type except age. Hence, from initial analysis we cannot say anything about this dataset.
```{r}
library(colorDF)
c=colorDF(Bone_Tumor, theme="bw")
c
```
## Selecting a sample
```{r}
grade_s=sample(Bone_Tumor$Grade,150,replace=FALSE)
class(grade_s)
```
```{r}
?count
```
count works when the first variable is a dataframe.

```{r}
library(dplyr)


```
```{r}
#Another way of taking a sample
grade_s=sample(1:nrow(Bone_Tumor),150,replace=FALSE)
grade_s
class(grade_s)
```
Above are serial numbers, so basicaly we get the entire row for study.
```{r}
new<- Bone_Tumor[grade_s,3] # 3 represents col number, so this extracts all values from 3 rd column based on the row numbers in grade_s
new
class(new)
```

```{r}
#Converting sample to dataframe
df<- Bone_Tumor[grade_s,]
df
class(df)
```

Target variable=Grade of Bone tumor
```{r}
count(df,Grade)

```
```{r}
count(df,Grade,Sex)

```
## Sample Proportion
```{r}
#proportion=x/n
63/150
```
Sample proportion of high grade tumors is 0.42.

## Setting Hypothesis
P0:Proportion of high grade tumors
# Assuming population proportion
H0: P0 = 0.45
H1: P0! = 0.45
```{r}
?prop.test
```


```{r}
x=63
n=150
prop.test(x,n,p=0.45,alternative="two.sided",conf.level = 0.99)
```
Since p>0.01, We fail to reject H0.
Therefore proportion of high grade tumors in the population is 0.45.
## VISUALIZATION

```{r}
library(ggplot2)
?ggplot2

ggplot(Bone_Tumor,aes(x=Grade))+geom_bar()

ggplot(Bone_Tumor,aes(x=Grade,fill=Sex))+geom_bar(colour="yellow")
```
```{r}
?geom_bar
?aes
```
## BINOM TEST

```{r}
?binom.test
binom.test(x, n, p = 0.45,alternative = "two.sided",conf.level = 0.99)
```


## ALTERNATIVE METHOD TO GET SAMPLE

```{r}

samp=sample(Bone_Tumor$Grade,150,replace = FALSE)

class(samp)

g<-as.data.frame(samp)
g


count(g,samp)
```
