---
title: "Lab 05"
author: "Jyosna Philip"
date: "2023-12-19"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## AIM
To test the equality of two population proportion

## DATASET DESCRIPTION
This dataset contains information on bone tumors. The data was collected from patients at the Memorial Sloan Kettering Cancer Center (MSKCC). 
```{r cars}
Bone_Tumor <- read.csv("C:/Users/jyosn/Downloads/archive (1)/Bone Tumor Dataset.csv")

```
## ANALYSIS
```{r}
head(Bone_Tumor)
tail(Bone_Tumor)
```
## CREATING 2 POPULATIONS

```{r}
##Population 1
male<- subset(Bone_Tumor, Sex =="Male")

```

```{r}
#Population 2
female<- subset(Bone_Tumor, Sex =="Female")
```

## TO CHECK HYPOTHESIS 

Taking the Sample

```{r}
sm=sample(male$Grade,150,replace = FALSE)
S1=as.data.frame(sm) #to convert to dataframe

sf=sample(female$Grade,150,replace = FALSE)
S2=as.data.frame(sf)
S2
```


## COUNT OF THE SAMPLE

```{r}
library(dplyr)
count(S1,sm)
count(S2,sf)
```

## FIXING PROPORTION

P0: proportion of  High Grade Tumors in Male
P1: proportion of High Grade Tumors in Female
## assume the population propotion
H0: P0 = P1
H1: P0 != P1

Success = 110 High Grade Tumors in Male
Success = 28 Current High Grade Tumors in Female

```{r}
?c
?prop.test
```


```{r}
x1=c(110,28)   #x1 has the success rates
n1=c(150,150)   #n1 has the sample sizes
prop.test(x1, n1, alternative = "two.sided", conf.level = 0.99)
```
We get a very small p-value<0.01.
Hence we have to reject H0.
Therefore the true proportion of males and females with high grade bone tumors is not equal.
We can now move forward to the one sided test.

## ONE SIDED TEST

## RIGHT-SIDED TEST
H0: P0 = P1
H1: P0 > P1
Alternative hypothesis:True Proportion of High grade tumors in males is greater than that of females.

```{r}
prop.test(x1, n1, alternative = "greater", conf.level = 0.99)
```
We get a p-value which is very less than 0.01.
Hence, we can reject H0 and conclude that that P0>P1.

## Conclusion

Our rejection og null hypothesis in the two-sided test led us to carrying out the right-sided test. P-value obtained was less than 0.01, and so we rejected our null hypothesis. As a result our alternative hypothesis is accepted. Thus, the true proportion of males with high grade bone tumor is more than the true proportion of females with high grade bone tumor.






 