---
title: "Lab 02"
author: "Jyosna Philip"
date: "2023-12-04"
output: word_document
---
# Dataset Description

This dataset includes a record of the date, time, location, depth, magnitude, and source of every earthquake with a reported magnitude 5.5 or higher from 1965-2016.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
earthquakes <- read.csv("C:/Users/jyosn/Downloads/database.csv/database.csv")
head(earthquakes)
tail(earthquakes)
```

Our target variable is Magnitude i.e, the magnitude of the Earthquake.
```{r}
dim(earthquakes)

```
Thus there are 23412 observations(rows) and 21 attributes(columns).
```{r}
mean(earthquakes$Magnitude)
sd(earthquakes$Magnitude)
```
Thus the population mean is 5.88 and population sd is 0.42.

# Sample
```{r}
s=sample(earthquakes$Magnitude,100,replace=FALSE)
mean(s)
```
```{r}
sd_s=sd(s)
sd_s
```
Thus the sample population mean is 5.81 and sample sd is 0.35.

## TWO SIDED HYPOTHESIS TEST
# To test whether the avg earthquake magnitude is 5.81 or not.

H0: mean=5.86
H1: mean!=5.86
```{r}
library(BSDA)
z.test(x=s,alternative="two.sided",mu=5.86,sigma.x=sd_s,conf.level=0.95)
```
The z-value is -1.43 which is greater than the critical value at 0.95 confidence level.
Also p-value is 0.1528 which is greater than than 0.05, hence we fail to reject H0.
Conclusion: The mean magnitude of Earthquakes from 1965-2016(if they were above 5.5) is 5.86 .

# LEFT-TAILED HYPOTHESIS TEST
 To test whether the average magnitude of earthquakes is 5.86 or less than it.
H0: mean=5.86
H1: mean<5.86

```{r}
z.test(x=s,alternative="less",mu=5.86,sigma.x=sd_s,conf.level=0.95)
```
The z-value is -1.43 which is greater than -1.46. -1.46 is the critical value at 5% significance level for left-tailed test. Also p-value is 0.076 which is greater than than 0.05. Hence we fail to reject H0.
Conclusion: The mean magnitude of Earthquakes from 1965-2016(if they were above 5.5) is 5.86 .

# RIGHT-TAILED HYPOTHESIS TEST
 To test whether the average magnitude of earthquakes is 5.86 or greater than it.
H0: mean=5.86
H1: mean>5.86

```{r}
z.test(x=s,alternative="greater",mu=5.86,sigma.x=sd_s,conf.level=0.95)
```
The z-value is -1.43 which is less than 1.46. 1.46 is the critical value at 5% significance level for right-tailed test. Also p-value is 0.924 which is  much greater than than 0.05. Hence we fail to reject H0.
Conclusion: The mean magnitude of Earthquakes from 1965-2016(if they were above 5.5) is 5.86 .


