---
title: "Lab 06"
author: "Jyosna Philip"
date: "2024-01-03"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# About the dataset

This dataset contains online shopping data. It includes categorical variables like Gender,Coupon Status and Location.

```{r}
online_shopping <- read.csv("C:/Users/jyosn/Downloads/archive (2)/online_shopping.csv")


online_shopping<- na.omit(online_shopping)


dim(online_shopping)
```
The dataset has 21 columns and 52524 entries.

```{r}
summary(online_shopping)
```
We can see that the continuous variables are Avg_Price, Delivery_Charges,GST, Online_Spend,Offline_Spend.
On the other hand we have categorical variables Gender, Location, Tenure_Months, Coupon_Status.
Avg_Price ranges from 0.39 to 355.74. Delivery_Charges ranges from 0 to 521.36.
GST ranges from 0.05 to 0.18
Offline_Spend ranges from 500 to 5000.
Online_Spend ranges from 320.2 to 4556.9.


5.AIM:Perform the visualization for all categorical and target variables

Categorical variables are Gender, Location, Tenure_Months, Coupon_Status
```{r}
library(ggplot2)
```

```{r}
#visualisation for categorical variable : Gender
ggplot(online_shopping,aes(x=Gender))+geom_bar()
```
```{r}
#visualisation for categorical variable : Location
ggplot(online_shopping,aes(x=Location))+geom_bar()
#Visualisation for gender and Location
ggplot(online_shopping,aes(x=Gender,fill=Location))+geom_bar()
ggplot(online_shopping,aes(x=Location,fill=Gender))+geom_bar()
```
```{r}
#visualisation for categorical variable : Coupon Status
ggplot(online_shopping,aes(x=Coupon_Status))+geom_bar()
#visualisation for coupon status and gender
ggplot(online_shopping,aes(x=Gender,fill=Coupon_Status))+geom_bar()
```
```{r}
#visualisation for categorical variable :Tenure_Months
ggplot(online_shopping,aes(x=Tenure_Months))+geom_bar()
#visualisation for Tenure_Months and Gender
ggplot(online_shopping,aes(x=Tenure_Months,fill=Gender))+geom_bar()

```
```{r}
#Visualisation for target variable: Avg_Price
hist(online_shopping$Avg_Price,xlab="Avg_price",ylab="Frequency")
```


_________________________________________________________________________________________________________________________________
7.  AIM: Perform the single proportion test when σ is known and interpret the results.

Our target variable is average_price
```{r}
mean(online_shopping$Avg_Price)
sd(online_shopping$Avg_Price)
```
Hence, the mean and standard deviation of avg_price is 52.4 and 64.1 respectively.

```{r}
s=sample(online_shopping$Avg_Price,100,replace = FALSE)
mean(s)
```
The mean of sample is 48.77.
```{r}
sd_s=sd(s)
sd_s
```
The standard deviation of the sample is 63.62.

TWO-SIDED HYPOTHESIS TEST
H0:mu=51
H1: mu!=51

```{r}
library(BSDA)
z.test(x=s,alternative="two.sided",mu=51,sigma.x=sd_s,conf.level=0.95)
```
p-value is greater than 0.05. Hence we fail to reject H0. We can conclude that population mean is 51.

Conclusion: The population mean of Avg_Price is 51.



_________________________________________________________________________________________________________________________________

 8. Let’s consider an assertion that states 30% of students prefer online learning. A
survey was conducted among a random sample of 600 students, revealing that 180
students favour online learning. Can we validate this claim at a 5% significance
level based on the sample data?

AIM: To carry out single proportion test when variance is unknown
Let P0=Proportion of students favouring online learning

H0: P0=0.3
H1: P0 != 0.3


```{r}
n=600
x=180
prop.test(x,n,p=0.3,alternative = "two.sided",conf.level = 0.05)
```
Here p-value =1
p-value>0.05,Hence we fail to reject H0.

Conclusion:
We can validate the claim that 30% students prefer online learning.
_________________________________________________________________________________________________________________________________
