---
title: "Lab_10"
author: "Jyosna Philip"
date: "2024-02-09"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1) Movie data:
A)Test whether the genre and main production company of a movie is having any significant effect on the the IMDB score.
B)If the score is affected due to the genre or production company, perform appropriate test to find out for which genre or which production company it is differing. [use multiple pairwise comparison test]
2) For the given nike data, test whether the average price of nike products that are in stock and out of stock are significantly differing or not.[ Note: Check the assumptions first]

3)Take a sample of 250 from the population and test whether the variance of price of nike products is 45. Validate using an appropriate test.
4)Test whether the proportion of nike products that are in white, black, Navy are significantly different or not.

1. AIM : To test whether the genre and main production company of a movie is having any significant effect on the the IMDB score.

```{r}
library(readxl)
Movie<- read_excel("C:/Users/jyosn/Downloads/Best Movie by Year Netflix.xlsx")

```

# About the dataset.
This dataset contains the best movies on IMDB from 1954 to 2021. It has 49 rows and 5 attributes.
```{r}
head(Movie)
```
We carry out TWO-WAY ANOVA TEST as we have to check whether two attributes (with more than 2 levels) have an effect on the IMDB score.


```{r}
#extract variables
genre<-Movie$MAIN_GENRE
production<- Movie$MAIN_PRODUCTION
```

```{r}
genre<-as.factor(genre)
production<-as.factor(production)
levels(genre)
levels(production)
```
Therefore the two attributes have:
Genre: it has 12 levels
production: it has 7 levels

We try this with both 'With interaction' and 'without interaction'.

# WITHOUT INTERACTION
**Define hypothesis**

Ha0: Genre has no significant effect on the IMDB Score.
Ha1: Genre has significant effect on the IMDB Score.
      
Hb0: main production company has no significant effect on the IMDB Score.
Hb1:  main production company has significant effect on the IMDB Score.
```{r}
result<-aov(Movie$SCORE~genre+production,data=Movie)
result
```

```{r}
summary(result)
```
Since p-values for both genre and production is greater than 0.05, we accept Ha0 and Hb0.
Hence,  Genre has no significant effect on the IMDB Score. Also Production company has no significant effect on IMDB Score.

# **WITH INTERACTION EFFECT**

1. **Defining the null and alternative hypothesis**:     
Ha0: There is no significant difference in the score of movies with difference in genre.
Ha1: There is a significant difference in the score of movies with difference in genre.

Hb0:  There is no significant difference in the score of movies with difference in production company.
Hb1:  There is a significant difference in the score of movies with difference in production company.

Hc0: There is no interaction effect
Hc1: There is an interaction effect

```{r}
result1<-aov(Movie$SCORE~genre*production,data=Movie)
summary(result1)
```
All p-values obtained in this test is greater than 0.05. 
Hence we fail to reject Ha0,Hb0,Hc0.
There is no significant effect on the score of movies due to their genre or production company. there is no interaction effect between genre and production company.

2) AIM: Test whether the average price of nike products that are in stock and out of stock are significantly differing or not.

```{r}
library(readxl)
```

```{r}

nike<- read_excel("C:/Users/jyosn/Downloads/nike_data_2022_09.xlsx")
head(nike)

```
```{r}
availability<-as.factor(nike$availability)
levels(availability)
```

Since availability attribute has only two levels, and we need to find the average mean of both types, we carry out the z test for equality of two means .

**HYPOTHESIS**

H0:average price of nike products that are in stock and out of stock are NOT significantly different. mu1=mu2
H1:average price of nike products that are in stock and out of stock are  significantly different. mu1!=mu2


```{r}
stock<-subset(nike,availability=='InStock')
not_instock<-subset(nike,availability==c('OutOfStock'))
stock
```
```{r}
stock_sample<-sample(stock$price,100,replace=TRUE)
outOfStock_sample<-sample(not_instock$price,100,replace=TRUE)

```

```{r}
mean_stock<-mean(stock_sample)
mean_notInStock<-mean(outOfStock_sample)
sd_stock<-sd(stock_sample)
sd_notInStock<-sd(outOfStock_sample)
```
```{r}
mean_stock
mean_notInStock
sd_stock
sd_notInStock
```

```{r}
library(BSDA)
```
```{r}
z.test(x=stock_sample,y=outOfStock_sample,alternative='two.sided',mu=0,sigma.x=sd_stock,sigma.y=sd_notInStock,conf.level = 0.95)
```
Since the p-value is less than 0.05, we reject H0. Hence the price of instock items and items not in stock are significantly different.

**RIGHT-SIDED TEST**

H0:average price of nike products that are in stock and out of stock are NOT significantly different. mu1=mu2
H1:average price of nike products that are in stock is significantly greater than that of  out of stock . mu1<mu2
```{r}
z.test(x=stock_sample,y=outOfStock_sample,alternative='greater',mu=0,sigma.x=sd_stock,sigma.y=sd_notInStock,conf.level = 0.95)
```
since p-value is less than 0.05, we reject H0.
Hence, average price of nike products that are in stock is significantly greater than that of  out of stock . mu1<mu2

**Conclusion**
A z-test was carried out to check whether the average price of products instock significantly differed from that which were out of stock. Results show that the average price of products in stock are signifcantly greater than that which are out of stock.

**Answer3:**
```{r}
sample1<-sample(nike,size=250,replace=TRUE)

```
We need to check whether the variance in price is 45. We need to carry out chi square test for this.

**Importing required library**
```{r}
library(EnvStats)
```
Here our target variable is price

# CHI SQUARE TEST FOR SINGLE VARIANCE
H0: The variance of price of nike products is 45
H1: The variance of price of nike products is not 45

**Setting significance level**
$\alpha$=0.05

**Two tailed test **
```{r}
varTest(sample1$price,alternative = "two.sided",sigma.squared =45)
```
We have obtained a p-value less tha 0.05 i.e., 0.
Hence we reject H0 and conclude that the variance of nike products is not 45

**Right sided test**
H0: The variance of price of nike products is 45
H1: The variance of price of nike products is greater than 45

```{r}
varTest(sample1$price,alternative = "greater",sigma.squared =45)
```
We obtain a p-value of 0. Hence we reject H0 and conclude that the variance of nike product price is greater than 45.

**Conclusion**
A chi-square test for single variance was used to check whether the variance of nike products price was 45. Followed by the rejection of null hypothesis in two tailed test, a right tatiled test was conducted to confirm that the nike product price variance is greater than 45.

**Ans 4**
# AIM: 
   To check whether the proportion of nike products in white,black and navy are same or not.
   
For this we need to use prop.test
```{r}
library(dplyr)
```
**Setting up hypothesis**
H0: The proportion of black, navy and white products are same.
H1: The proportion of black, navy and white products are not same.

**Setting the significance level**
$\alpha$=0.05 
```{r}
nike_df<-as.data.frame((nike))
colors<- subset(nike_df, nike_df$color %in% c("White","Black","Navy","Black/Black","White/White","Navy/Navy"),color)
colors
```
```{r}
count(colors,color)
count(nike_df)
```
```{r}
x=c(16,3,9) #number of black, navy, and white products respectively

n=c(112,112,112) #total number of products
prop.test(x, n, alternative = "two.sided", conf.level = 0.95)

```
We got a p-value less than 0.05. Hence we reject H0 and conclude that atleast on among the  proportion of black, navy and white nike products are significantly different.

```{r}
#checking proportion of black and white products
#Ha0:The proportion of black, and white products are same.
#Ha1: The proportion of black, and white products are not same.
x=c(16,9) #number of black,and white products respectively

n=c(112,112) #total number of products
prop.test(x, n, alternative = "two.sided", conf.level = 0.95)
```
The p-value is greater than 0.05 hence we fail to reject Ha0 and conclude that the proprotion of white and black products are not signifcantly different.
```{r}
#checking proportion of white and navy products
#Hb0:The proportion of white, and navy products are same.
#Hb1: The proportion of white, and navy products are not same.
x=c(9,3) #number of white,and navy products respectively

n=c(112,112) #total number of products
prop.test(x, n, alternative = "two.sided", conf.level = 0.95)
```
The p-value is greater than 0.05 hence we fail to reject Hb0 and conclude that the proportion of white and navy products are not significantly different.

```{r}
#checking proportion of black and navy products
#Hc0:The proportion of black, and navy products are same.
#Hc1: The proportion of black, and navy products are not same.
x=c(16,3) #number of black,and navy products respectively

n=c(112,112) #total number of products
prop.test(x, n, alternative = "two.sided", conf.level = 0.95)
```
The p-value is less  than 0.05 hence we  reject Hc0 and conclude that the proportion of navy and black products are significantly different.

**Right tailed test for proportion of navy and black products**

```{r}

#Hd0:The proportion of black, and navy products are same.
#Hd1: The proportion of black products is greater than that of navy products.

prop.test(x, n, alternative = "greater", conf.level = 0.95)
```
Our p-value is less than 0.05 and hence we can reject Hd0. therefore the proportion of Black products is significantly greater than that of navy products.

**Conclusion**
We did 3 sample proportion test to check whether the proportion of black, white and navy products are the same. our intitial test resulted in rejection of H0. therefore at least one pair of color had significantly different proportions. Further tests proved that that the proportion of black products were significantly greater than that of navy products. On the other hand, we also found that proportion of black and white products and the proportion of navy and white products are not significantly different.





